---
title: "README"
output: md_document
---

At the end of 2013, I decided prior to beginning my junior year at the University of Pennsylvania that I'd wanted to be an actuary. One of the many compelling forces that had brought me to this particular career strategy was the widely cited career outlook for actuaries around that period of time. For example, from [BeAnActuary.org]():

Look at all that press. But.. it sure is a little stale. So I took to the web to see how the "Actuary" career was faring in the same career ranking site that was boasting top billing for the profession that I love. And, well, things have changed.


```{r get_data_2019}

library(tidyverse)
library(rvest)
library(xml2)

scrape_careercast_page <- function(url) 
{
  # Scrape HTML file from 2019 job report
  
  rankings_html <- read_html(url)
  
  get_rankings_data <- as_list(xml2::xml_find_all(rankings_html,'//*[contains(concat( " ", @class, " " ), concat( " ", "aiNormalizedNumber", " " ))] | //*[contains(concat( " ", @class, " " ), concat( " ", "views-field-field-name", " " ))]')) %>% 
    flatten() %>% 
    flatten() %>% 
    flatten() %>% 
    tibble(data = str_trim(.)) %>% 
    select(data) %>% 
    filter(data != "") %>% 
    mutate(n = (row_number() - 1) %% 6,
           label = case_when(n == 0 ~ "rank",
                             n == 1 ~ "career",
                             n == 2 ~ "overall_rank",
                             n == 3 ~ "work_environment_rank",
                             n == 4 ~ "stress_rank",
                             n == 5 ~ "proj_growth_rank")) %>% 
    filter(n != 0) %>% 
    arrange(n) %>% 
    mutate(n = (row_number() - 1) %% 20) %>% 
    group_by(n) %>% 
    pivot_wider(names_from = label, values_from = data) %>% 
    ungroup() %>% 
    select(-n)

    return(get_rankings_data)  
}

rankings_url <- "https://www.careercast.com/jobs-rated/2019-jobs-rated-report?page=0"
scrape_careercast_page(rankings_url)
  
```

There's a reason I made this a function - it's so I could scrape the CareerCast site from the last ten years, and see what careers have risen and fallen in their ranking methodology, which has remained completely consistent and stable over the last decade. My only hope is that their web design philosophy and CSS naming conventions have remained just as consistent!

Since it's only ten years, I've chosen to do it by hand, but if we were doing any more than a decade, this is the kind of stuff `purrr::map()` is made for.

```{r pull_decade}

# 2019
rankings_url <- "https://www.careercast.com/jobs-rated/2019-jobs-rated-report?page=0"
data <- scrape_careercast_page(rankings_url) %>% 
  mutate(year = 2019)

# 2018 - there is an issue here that has the overall ranking starting at 2 instead of 1. I've corrected for this.
rankings_url <- "https://www.careercast.com/jobs-rated/2018-jobs-rated-report"
data2018 <- scrape_careercast_page(rankings_url) %>% 
  mutate(year = 2018)
  
data2018 <- data2018 %>% 
  separate(overall_rank,  sep="/", into=c("num","den")) %>% 
  mutate(num = as.character(as.numeric(num) - 1)) %>% 
  unite(col="overall_rank", num, den, sep="/")

data <- data %>% 
  union_all(data2018)

# 2017 - no issues
rankings_url <- "https://www.careercast.com/jobs-rated/2017-jobs-rated-report"
data2017 <- scrape_careercast_page(rankings_url) %>% 
  mutate(year = 2017)

data <- data %>% 
  union_all(data2017)

# 2016 - URL format is slightly different.
rankings_url <- "https://www.careercast.com/jobs-rated/jobs-rated-report-2016-ranking-200-jobs"
data2016 <- scrape_careercast_page(rankings_url) %>% 
  mutate(year = 2016)

data <- data %>% 
  union_all(data2016)

# 2015 - again slightly different URL
rankings_url <- "https://www.careercast.com/jobs-rated/jobs-rated-report-2015-ranking-top-200-jobs"
data2015 <- scrape_careercast_page(rankings_url) %>% 
  mutate(year = 2015)

data <- data %>% 
  union_all(data2015)

# 2014 - again a slightly different URL
rankings_url <- "https://www.careercast.com/jobs-rated/jobs-rated-2014-ranking-200-jobs-best-worst"
data2014 <- scrape_careercast_page(rankings_url) %>% 
  mutate(year = 2014)

data <- data %>% 
  union_all(data2014)

# 2013 - again a slightly different URL than last year
rankings_url <- "https://www.careercast.com/jobs-rated/best-worst-jobs-2013"
data2013 <- scrape_careercast_page(rankings_url) %>% 
  mutate(year = 2013)

data <- data %>% 
  union_all(data2013)

# 2012 - again a slightly different URL than last year
rankings_url <- "https://www.careercast.com/jobs-rated/2012-ranking-200-jobs-best-worst"
data2012 <- scrape_careercast_page(rankings_url) %>% 
  mutate(year = 2012)

data <- data %>% 
  union_all(data2012)

# 2011 - the same URL format as the 2012 report! huzzah!
rankings_url <- "https://www.careercast.com/jobs-rated/2011-ranking-200-jobs-best-worst"
data2011 <- scrape_careercast_page(rankings_url) %>% 
  mutate(year = 2011)

data <- data %>% 
  union_all(data2011)

# 2010 is a 404 error, so we'll stop there.
```


```{r plotting}

# As usual, we'll set up a plot function that gives a plot of the ranking we want - overall,
# job growth, stress, etc.

plotRanking <- function(metric)
{
  
  metricLabel = ifelse(metric == "overall_rank","Overall Rank",
                 ifelse(metric == "work_environment_rank","Work Environment Rank",
                        ifelse(metric == "stress_rank","Stress Rank", "Projected Growth Rank")))
  
  plot.data <- data %>% 
    select(career, eval(metric), year) %>% 
    separate(eval(metric), into=c("num","denom"), sep="/") %>% 
    mutate(num = as.numeric(num))
  
  plot.data <- plot.data %>% 
    group_by(career) %>% 
    summarize(n = n()) %>% 
    filter(n >= 4) %>% 
    left_join(plot.data)
  
  plot <- plot.data %>% 
    ggplot(aes(x = year, y = num, color = career)) + 
    geom_line(size = 1.5) +
    geom_point(size = 2) + 
    scale_y_reverse(labels = scales::label_ordinal(), breaks=seq(1:20)) +
    labs(x = "Year",
         y = "Rank",
         title = paste0(metricLabel, " over the Last Decade-ish"),
         subtitle = "CareerCast.com Career Rankings, 2011 - 2019") +
    theme_minimal()
    
  plot
}

plotRanking("overall_rank")

```

